Supplementary methods

### 2020-08-28 text/supplemental_methods.Rmd
Added graphs for priors for the ktis and kclass, as well as some text

---
title: "Supplementary methods"
author: "Peter T. Nguyen, Simon G. Coetzee, Daniel L. Lakeland, and Dennis J. Hazelett"
date: "8/24/2020"
bibliography: references.bib
output:
  word_document:
    reference_docx: "../text/word-style-reference-ttmanu.docx"
always_allow_html: TRUE
editor_options:
  chunk_output_type: console
---

@@

>>>>

---
title: "Supplementary methods"
author: "Peter T. Nguyen, Simon G. Coetzee, Daniel L. Lakeland, and Dennis J. Hazelett"
bibliography: references.bib
output:
  word_document:
    reference_docx: "../text/word-style-reference-ttmanu.docx"
always_allow_html: TRUE
editor_options:
  chunk_output_type: console
---

@@

### Figure SM3
```{r}

pritis = ggplot(data.frame(x=0:30),aes(x)) + stat_function(fun=function(x) dgamma(x,1.2,.2),geom="area",fill="#666699")+
coord_cartesian(xlim=c(0,20),ylim=c(0,1))+labs(title="Prior for ktis",x="ktis")
pricl = ggplot(data.frame(x=0:30),aes(x)) + stat_function(fun=function(x) dgamma(x,3.5,2.5),geom="area",fill="#666699")+
coord_cartesian(xlim=c(0,20),ylim=c(0,1))+labs(title="Prior for kclass",x="kclass")
print(pritis+pricl)

```

Priors for the tissue and class coefficients. The tissue coefficient
is chosen to admit parameter values across a range from near 0 to 20+
in the high density region, reflecting the wide variety of severities
across tissue type. Within a given tissue, the class k parameter
multiplies the tissue k and is given a peak density at 1, and a
credible range from near 0 to 5, reflecting our expectation of a
moderate amount of variation across the classes.
